---
title: "NICAR 2026 Session Explorer"
format:
  html:
    page-layout: full
    toc: false
    theme: flatly
    css: styles.css
    include-in-header:
      text: |
        <link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/6.4.0/css/all.min.css">
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(arrow)
library(dplyr)
library(reactable)
library(htmltools)
library(htmlwidgets)

sessions_data <- read_parquet("sessions_info_for_app.parquet")
```

::: {.header-section}
::: {.header-content}
<a href="https://github.com/smach/NICAR2026_chatbot" target="_blank" title="View source on GitHub" class="github-link"><i class="fa-brands fa-github"></i></a>

# NICAR 2026 Session Explorer

AI-Powered Session Discovery • 📍 Indianapolis, March 5-8, 2026

::: {.header-note}
⚠️ AI can make mistakes - verify on the [official schedule](https://schedules.ire.org/nicar-2026/)
:::
:::
:::

::: {.app-layout}

::: {.chat-sidebar}
::: {.inactive-notice}
## 🤖 Chatbot No Longer Active

::: {.inactive-big-text}
The AI chatbot is no longer running.
:::

::: {.inactive-explanation}
To save on hosting and API costs, Sharon has taken the live chatbot offline.

**Good news:** the full app is open source. You can view all the code on GitHub and run the chatbot yourself with your own (free-tier) Google Gemini API key.
:::

::: {.inactive-actions}
<a href="https://github.com/smach/NICAR2026_chatbot" target="_blank" class="btn-conference">
  <i class="fa-brands fa-github"></i> View code on GitHub (main branch)
</a>

<a href="https://github.com/smach/NICAR2026_chatbot#readme" target="_blank" class="btn-secondary">
  📖 Setup instructions
</a>
:::

::: {.inactive-footnote}
The searchable session table on the right is still fully available.
:::
:::
:::

::: {.main-panel}

::: {.table-header}
::: {.table-header-left}
### 📚 Session Directory

Click any session for details • Search to filter • All descriptions are searchable
:::

::: {.stats-box}
```{r stats}
total <- nrow(sessions_data)
thu <- sum(sessions_data$Day == "Thursday", na.rm = TRUE)
fri <- sum(sessions_data$Day == "Friday", na.rm = TRUE)
sat <- sum(sessions_data$Day == "Saturday", na.rm = TRUE)
sun <- sum(sessions_data$Day == "Sunday", na.rm = TRUE)
HTML(paste0(
  "📊 ", total, " Total Sessions<br>",
  "Thu: ", thu, " | Fri: ", fri, " | Sat: ", sat, " | Sun: ", sun
))
```
:::
:::

```{r session-table}
table_theme <- reactableTheme(
  searchInputStyle = list(
    width = "100%",
    backgroundColor = "#ffffff",
    border = "2px solid #e0e0e0",
    borderRadius = "4px",
    padding = "8px 12px",
    fontSize = "14px"
  ),
  headerStyle = list(
    background = "#A8C6C4",
    color = "#2B4C5E",
    fontWeight = "600",
    fontSize = "14px"
  ),
  rowStyle = list(
    cursor = "pointer",
    "&:hover" = list(background = "#f0f8f6")
  )
)

reactable(
  sessions_data,
  columns = list(
    Title = colDef(
      name = "Session Title",
      minWidth = 280,
      class = "cell-title"
    ),
    Day = colDef(
      name = "Day",
      width = 110,
      sortable = FALSE,
      class = function(value) paste0("day-", tolower(value))
    ),
    Time = colDef(
      name = "Time",
      width = 85,
      sortable = FALSE,
      class = "cell-time"
    ),
    Speakers = colDef(
      name = "Speakers",
      minWidth = 180,
      class = "cell-speakers"
    ),
    Room = colDef(
      name = "Room",
      width = 100,
      class = "cell-room"
    ),
    Recorded = colDef(
      name = "Recorded",
      width = 80,
      align = "center",
      filterable = TRUE,
      filterInput = function(values, name) {
        tags$select(
          onchange = sprintf(
            "Reactable.setFilter('session-table', '%s', event.target.value || undefined)",
            name
          ),
          tags$option(value = "", "All"),
          tags$option(value = "true", "Yes"),
          tags$option(value = "false", "No")
        )
      },
      filterMethod = JS(
        "function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            if (filterValue === 'true') return row.values[columnId] === true;
            if (filterValue === 'false') return row.values[columnId] === false;
            return true;
          })
        }"
      ),
      cell = function(value) {
        if (isTRUE(value)) {
          span(style = "color: #28a745;", "Yes")
        } else {
          span(style = "color: #dc3545;", "No")
        }
      }
    ),
    SkillLevel = colDef(
      name = "Skill Level",
      width = 100,
      class = "cell-skill"
    ),
    Track = colDef(
      name = "Track",
      width = 150,
      class = "cell-track"
    ),
    Description = colDef(show = FALSE, searchable = TRUE),
    Date = colDef(show = FALSE),
    Time_24hr = colDef(show = FALSE),
    Cost = colDef(show = FALSE),
    Type = colDef(show = FALSE)
  ),
  details = function(index) {
    session <- sessions_data[index, ]
    div(
      style = "padding: 20px; background: #f8f9fa; border-left: 4px solid #8FB339;",
      h4(
        session$Title,
        style = "color: #2B4C5E; margin-top: 0; font-weight: 600;"
      ),
      div(
        style = "margin-bottom: 15px; padding: 15px; background: white; border-radius: 5px;",
        p(
          session$Description,
          style = "line-height: 1.6; color: #333; margin: 0;"
        )
      ),
      div(
        style = "display: grid; grid-template-columns: auto 1fr; gap: 10px; margin-bottom: 15px;",
        tags$span(strong("Date:"), style = "color: #666;"),
        tags$span(paste(session$Day, "-", session$Date)),
        tags$span(strong("Type:"), style = "color: #666;"),
        tags$span(
          if (is.na(session$Type) || session$Type == "") {
            "Not specified"
          } else {
            session$Type
          }
        ),
        tags$span(strong("Cost:"), style = "color: #666;"),
        tags$span(
          if (is.na(session$Cost) || session$Cost == "") {
            "Free / Included"
          } else {
            paste0("$", session$Cost)
          }
        ),
        tags$span(strong("Recorded:"), style = "color: #666;"),
        tags$span(
          if (isTRUE(session$Recorded)) {
            "Yes - session will be recorded"
          } else {
            "No"
          }
        )
      ),
      div(
        style = "margin-top: 15px; text-align: right;",
        a(
          "View in official schedule",
          href = "https://schedules.ire.org/nicar-2026/",
          target = "_blank",
          class = "btn btn-sm",
          style = "background-color: #8FB339; border-color: #8FB339; color: white;"
        )
      )
    )
  },
  searchable = TRUE,
  searchMethod = JS(
    "function(rows, columnIds, searchValue) {
      var pattern;
      var useRegex = true;
      try {
        pattern = new RegExp(searchValue, 'i');
      } catch (e) {
        useRegex = false;
      }
      return rows.filter(function(row) {
        return columnIds.some(function(columnId) {
          var cellValue = String(row.values[columnId]).toLowerCase();
          if (useRegex) {
            return pattern.test(cellValue);
          } else {
            return cellValue.includes(searchValue.toLowerCase());
          }
        })
      })
    }"
  ),
  language = reactableLang(
    searchPlaceholder = "Search (regex supported)"
  ),
  filterable = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  striped = FALSE,
  pagination = TRUE,
  defaultPageSize = 12,
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(12, 25, 50, 100),
  theme = table_theme,
  elementId = "session-table"
)
```

:::

:::

::: {.app-footer}
App by [Sharon Machlis](https://machlis.com) & Claude AI
:::
